---
title: "IIPT Treatment Components"
description: |
  IIPT treatment components for all treatment sites identified through our systematic review.
output: 
  distill::distill_article:
    toc: true
editor_options: 
  chunk_output_type: console
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl)
library(benelib)
library(gt)
```

<!-- After publication of the parent article, the identified treatment sites and respective treatment components will be published here. -->

Below are the treatment components for all 13 treatment sites we were able to identify. For information where these treatment sites are located and which articles were referenced for a respective site, see [below](#considered-articles).

# Components per Site

```{r, layout="l-body-outset"}
read_excel("Treatment components.xlsx") %>%
  janitor::clean_names() %>%
  fill(category) %>%
  mutate(
    across(au1:de13, ~ ifelse(. == 0, "", "\U2713"))
  ) %>%
  rename_with(~ snakecase::to_title_case(., abbreviations = c("DE", "CA", "UK", "AU", "US"))) %>%
  group_by(Category) %>%
  gt() %>%
  theme_gt_apa() %>%
  cols_label(
    "AU 1" = html("AU<br>1"),
    "UK 2" = html("UK<br>2"),
    "DE 3" = html("DE<br>3"),
    "US 4" = html("US<br>4"),
    "US 5" = html("US<br>5"),
    "UK 6" = html("UK<br>6"),
    "US 7" = html("US<br>7"),
    "US 8" = html("US<br>8"),
    "US 9" = html("US<br>9"),
    "US 10" = html("US<br>10"),
    "US 11" = html("US<br>11"),
    "CA 12" = html("CA<br>12"),
    "DE 13" = html("DE<br>13"),
  ) %>%
  tab_style(
    style = cell_text(indent = "20px"),
    locations = cells_body(columns = 2)
  ) %>%
  tab_style(
    style = cell_text(indent = "0px", weight = "bold"),
    locations = cells_row_groups()
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_column_labels()
  )
```

# Considered Articles {#considered-articles}

### AU (1)

Melbourne, Australia

@Chalkiadis.2001

### UK (2)

Bath, UK

@Eccleston.2003

### DE (3)

Datteln, Germany

@Dobe.2006, @Dobe.2011, @Dogan.2021, @Flack.2018, @Hechler.2010, @Hechler.2010b, @Hechler.2009, @Hechler.2014, @Hechler.2014b, @Hirschfeld.2013, @LopezLumbi.2021, @Ruhe.2017, @Stahlschmidt.2017, @Stahlschmidt.2018, @Zernikow.2018

### US (4)

Baltimore, USA

@Maynard.2010, @Robinson.2019

### US (5)

Boston, USA

@Erpelding.2016, @Logan.2012, @Logan.2015, @Mirek.2019, @Nelson.2019, @Randall.2021, @Randall.2018, @Shulman.2020, @Shulman.2020b, @Sieberg.2017, @Simons.2012, @Simons.2018

### UK (6)

Bath, UK

@GauntlettGilbert.2013, @Kemani.2018

### US (7)

Kansas City, USA

@Pielech.2018, @Scheufler.2021, @Weiss.2013

### US (8)

Cleveland, USA

@Banez.2014, @Benore.2015, @Buchannan.2018, @Evans.2016, @Kempert.2020, @Kempert.2017

### US (9)

Philadelphia, USA

@Sherry.2015, @Gmuca.13.06.2022

### US (10)

Cincinnati, USA

@Boggero.2021, @Krietsch.2021, @Williams.2020, @Williams.13.10.2022

### US (11)

Rochester, USA

@Bruce.2017, @Fahrenkamp.2020, @JunghansRutelonis.2018

### CA (12)

Calgary, Canada

@Hurtubise.2020b, @Rayner.11.10.2022

### DE (13)

Garmisch-Partenkirchen, Germany

@Hoefel.2016
